Stay in shape! Homework exam II

### 2016-04-03 geometricAlgorithms/homeworkExam/2/homeworkExam.tex
arguing

\subsection{Argue that all horizontal line segs are found}
All line segments are found because the binary search tree will
select as many as possible y based nodes and then ask the

>>>>

\subsection{Argue that all horizontal line segs are found}
All lines are found because the outer tree just selects based on the y range
as soon as a split node is encountered its starts reporting.
Then the $x$ interval tree will filter out all lines that are not on
the x at that level.
